### 2020-03-03 system-model.tex
:pencil: Received signal

            \begin{subsubsection} {Modulated Information Waveform}
                Assume the carrier are evenly spaced with equal bandwidth $B_s$ such that the frequency of the $n$-th subband is $f_n = f_0+(n-1) \Delta f$ ($n = 1,\dots,N$). The information symbol $\tilde{x}_{I,n}$ on subband $n$ is a capacity-achieving i.i.d. Circular Symmetric Complex Gaussian (CSCG) variable with zero mean and unit variance (i.e. $\tilde{x}_{I,n} \sim \mathcal{CN}(0,1)$). Denote $w_{I,n,m} = s_{I,n,m} e^{j\phi_{I,n,m}}$ as the information weight on the $n$-th subcarrier of the $m$-th ($m = 1,\dots,M$) transmit antenna with magnitude $s_{I,n,m}$ and phase $\phi_{I,n,m}$, the corresponding modulated symbol can be expressed as $x_{I,n,m} = \tilde{s}_{I,n,m} e^{j\tilde{\phi}_{I,n,m}}$, with $\tilde{s}_{I,n,m} = s_{I,n,m} \lvert\tilde{x}_{I,n}\rvert$ and $\tilde{\phi}_{I,n,m} = \phi_{I,n,m} + \angle{\tilde{x}_n}$, which also follows zero-mean CSCG distribution with variance equal to the subcarrier power (i.e. $x_{I,n,m} \sim \mathcal{CN}(0,s_{I,n,m}^2)$). Therefore, the transmit information waveform on the antenna $m$ at time $t$ writes as
                \begin{equation} \label{eq:x_{I,m}(t)}
                    \begin{split}
                        x_{I,m}(t)
                        &= \sum_{n=1}^{N} \tilde{s}_{I,n,m}(t) \cos \left( 2 \pi f_n t + \tilde{\phi}_{I,n,m}(t) \right) \\
                        &= \Re \left\{ \sum_{n=1}^{N} x_{I,n,m}(t) e^{j2 \pi f_n t} \right\} \\
                        &= \Re \left\{ \sum_{n=1}^{N} w_{I,n,m} \tilde{x}_{I,n}(t) e^{j2 \pi f_n t} \right\}
                    \end{split}
                \end{equation}
            \end{subsubsection}

            \begin{subsubsection} {Unmodulated Power Waveform}
                As suggested in \cite{Clerckx2018b,Clerckx2016a}, we use deterministic multisine waveform to boost the harvested energy. It has no randomness over time and the equivalent input power symbol $\tilde{x}_{P,n}$ is a constant on subband $n$ (i.e. $\tilde{x}_{P,n} = 1$). Therefore, on the $n$-th subcarrier of the $m$-th transmit antenna, the power weight $w_{P,n,m} = s_{P,n,m} e^{j\phi_{P,n,m}}$ represents the complex-valued sinewave (i.e. $x_{P,n,m}(t) = w_{P,n,m}$) in the baseband. The transmit power waveform on the antenna $m$ at time $t$ is given by
                \begin{equation} \label{eq:x{P,m}(t)}
                    \begin{split}
                        x_{P,m}(t)
                        &= \sum_{n=1}^{N} s_{P,n,m}(t) \cos \left( 2 \pi f_n t + \phi_{P,n,m}(t) \right) \\
                        &= \Re \left\{ \sum_{n=1}^{N} x_{P,n,m}(t) e^{j2 \pi f_n t} \right\} \\
                        &= \Re \left\{ \sum_{n=1}^{N} w_{P,n,m} e^{j2 \pi f_n t} \right\}
                    \end{split}
                \end{equation}
            \end{subsubsection}

            \begin{subsubsection} {Superposed Waveform}
                At time $t$, a superposition of the information and power waveform on antenna $m$ over subband $n$ writes as
                \begin{equation} \label{eq:x_{n,m}(t)}
                    \begin{split}
                        x_{n,m}(t)
                        &= x_{I,n,m}(t)+x_{P,n,m}(t) \\
                        &= w_{I,n,m} \tilde{x}_{I,n}(t)+w_{P,n,m}
                    \end{split}
                \end{equation}
                The transmitted signal on antenna $m$ at time $t$ is a summation over all subbands
                \begin{equation} \label{eq:x_m(t)}
                    \begin{split}
                        x_m(t)
                        &= x_{I,m}(t)+x_{P,m}(t) \\
                        &= \Re \left\{ \sum_{n=1}^{N} (w_{I,n,m} \tilde{x}_{I,n}(t)+w_{P,n,m}) e^{j2 \pi f_n t} \right\}
                    \end{split}
                \end{equation}
            \end{subsubsection}

@@

        \begin{subsection} {Composite Channel Model}
            Consider a single-IRS scenario in a multipath environment. The frequency response of the AP-user (i.e. direct) channel between antenna $m$ and user $k$ at subband $n$ is $h_{D,n,m,k} = \sum_{l_{D,k}=1}^{L_{D,k}} \alpha_{l_{D,k}} e^{j\left( -2 \pi f_n \tau_{l_{D,k}}+\varsigma_{l_{D,k},n,m,k} \right)}$, where $L_{D,k}$ is the number of paths in the direct link of user $k$, $\alpha_{l_{D,k}}$ and $\tau_{l_{D,k}}$ are the delay and amplitude gain of the $l_{D,k}$-th path, $\varsigma_{l_{D,k},n,m,k}$ is the phase shift of the $l_{D,k}$-path between transmit antenna $m$ and the receive antenna of user $k$ at subband $n$. Similarly, the AP-IRS (i.e. incident) channel between antenna $m$ and element $u$ at subband $n$ writes as $h_{I,n,m,u} = \sum_{l_{I,u}=1}^{L_{I,u}} \alpha_{l_{I,u}} e^{j\left( -2 \pi f_n \tau_{l_{I,u}}+\varsigma_{l_{I,u},n,m,u} \right)}$, and the IRS-user (i.e. reflective) channel between element $u$ and user $k$ is $h_{R,n,u,k} = \sum_{l_{R,k}=1}^{L_{R,k}} \alpha_{l_{R,k}} e^{j\left( -2 \pi f_n \tau_{l_{R,k}}+\varsigma_{l_{R,k},n,u,k} \right)}$. Assume that $\max_{l_{D,k} \neq l_{D,k}'} \lvert \tau_{l_{D,k}}-\tau_{l_{D,k}'} \rvert \ll 1/B_s$ and $\max_{l_{I,u},l_{R,k} \neq l_{I,u}',l_{R,k}'} \lvert \left( \tau_{l_{I,u}}+\tau_{l_{R,k}} \right)-\left( \tau_{l_{I,u}'}+\tau_{l_{R,k}'} \right) \rvert \ll 1/B_s$ such that $\tilde{x}_n(t)$ and $x_{n,m}(t)$ are narrowband signals, namely $\tilde{x}_n(t-\tau_{l_D}) = \tilde{x}_n(t-\tau_{l_{I}}-\tau_{l_R}) = \tilde{x}_n(t)$ and $x_{n,m}(t-\tau_{l_D}) = x_{n,m}(t-\tau_{l_{I}}-\tau_{l_R}) = x_{n,m}(t)$.

@@

        \begin{subsection} {Received Signal}
            In the signal received by user $k$, the component from transmit antenna $m$ captures the contribution of information and power waveforms through both direct and reflective links. It can be expressed as
            \begin{equation} \label{eq:y_{m,k}(t)}
                \begin{split}
                    y_{m,k}(t)
                    &= \Re \left\{ \sum_{n=1}^{N} \sum_{l_{D,k}=1}^{L_{D,k}} \alpha_{l_{D,k}} x_{n,m}(t-\tau_{l_{D,k}}) e^{j \left( -2 \pi f_n (t-\tau_{l_{D,k}})+\varsigma_{l_{D,k},n,m,k}\right) } \right\} \\
                    &\quad+ \Re \left\{ \sum_{n=1}^{N} \sum_{l_{R,k}=1}^{L_{R,k}} \sum_{u=1}^{U} \alpha_{l_{R,k}} r_u \alpha_{l_{I,u}} x_{n,m}(t-\tau_{l_{R,k}}-\tau_{l_{I,u}}) e^{j \left( -2 \pi f_n (t-\tau_{l_{R,k}}-\tau_{l_{I,u}})+\varsigma_{l_{R,k},n,u,k}+\varsigma_{l_{I,u},n,m,u}\right)} \right\} \\
                    &\approx \Re \left\{ \sum_{n=1}^{N} \sum_{u=1}^{U} (h_{D,n,m,k}(t)+h_{R,n,u,k}(t) r_u h_{I,n,m,u}(t)) x_{n,m}(t) e^{j2 \pi f_n t} \right\} \\
                    &= \Re \left\{ \sum_{n=1}^{N} \sum_{u=1}^{U} (h_{D,n,m,k}(t)+h_{R,n,u,k}(t) \beta_u e^{j\theta_u} h_{I,n,m,u}(t)) \left( w_{I,n,m} \tilde{x}_{I,n}(t)+w_{P,n,m} \right) e^{j2{\pi} {f_n}{t}} \right\}
                \end{split}
            \end{equation}

        \end{subsection}
    \end{section}

>>>>

            \begin{subsubsection} {Modulated Information Waveform}
                Assume the carrier are evenly spaced with equal bandwidth $B_s$ such that the frequency of the $n$-th subband is $f_n = f_0+(n-1) \Delta f$ ($n = 1,\dots,N$). The information symbol $\tilde{x}_{I,n}$ on subband $n$ is a capacity-achieving i.i.d. Circular Symmetric Complex Gaussian (CSCG) variable with zero mean and unit variance (i.e. $\tilde{x}_{I,n} \sim \mathcal{CN}(0,1)$). Denote $w_{I,n,m} = s_{I,n,m} e^{j\phi_{I,n,m}}$ as the information weight on the $n$-th subcarrier of the $m$-th ($m = 1,\dots,M$) transmit antenna with magnitude $s_{I,n,m}$ and phase $\phi_{I,n,m}$, the corresponding modulated symbol can be expressed as $x_{I,n,m} = \tilde{s}_{I,n,m} e^{j\tilde{\phi}_{I,n,m}}$, with $\tilde{s}_{I,n,m} = s_{I,n,m} \lvert\tilde{x}_{I,n}\rvert$ and $\tilde{\phi}_{I,n,m} = \phi_{I,n,m} + \angle{\tilde{x}_n}$, which also follows zero-mean CSCG distribution with variance equal to the subcarrier power (i.e. $x_{I,n,m} \sim \mathcal{CN}(0,s_{I,n,m}^2)$). Therefore, the transmit information waveform on the antenna $m$ at time $t$ writes as
                \begin{equation} \label{eq:x_{I,m}(t)}
                    \begin{split}
                        x_{I,m}(t)
                        &= \sum_{n=1}^{N} \tilde{s}_{I,n,m}(t) \cos \left( 2 \pi f_n t + \tilde{\phi}_{I,n,m}(t) \right) \\
                        &= \Re \left\{ \sum_{n=1}^{N} x_{I,n,m}(t) e^{j2 \pi f_n t} \right\} \\
                        &= \Re \left\{ \sum_{n=1}^{N} w_{I,n,m} \tilde{x}_{I,n}(t) e^{j2 \pi f_n t} \right\}
                    \end{split}
                \end{equation}
                On top of this, the information waveform vector is spread over $M$ antennas
                \begin{equation} \label{eq:x_I(t)}
                    \boldsymbol{x}_I(t) = \Re \left\{ \sum_{n=1}^{N} \boldsymbol{w}_{I,n}\tilde{x}_n(t) e^{j2{\pi}{f_n}t} \right\}
                \end{equation}
                where $\boldsymbol{w}_{I,n}=[w_{I,n,1},\dots,w_{I,n,M}]^T$.
            \end{subsubsection}

            \begin{subsubsection} {Unmodulated Power Waveform}
                As suggested in \cite{Clerckx2018b,Clerckx2016a}, we use deterministic multisine waveform to boost the harvested energy. It has no randomness over time and the equivalent input power symbol $\tilde{x}_{P,n}$ is a constant on subband $n$ (i.e. $\tilde{x}_{P,n} = 1$). Therefore, on the $n$-th subcarrier of the $m$-th transmit antenna, the power weight $w_{P,n,m} = s_{P,n,m} e^{j\phi_{P,n,m}}$ represents the complex-valued sinewave (i.e. $x_{P,n,m}(t) = w_{P,n,m}$) in the baseband. The transmit power waveform on the antenna $m$ at time $t$ is given by
                \begin{equation} \label{eq:x{P,m}(t)}
                    \begin{split}
                        x_{P,m}(t)
                        &= \sum_{n=1}^{N} s_{P,n,m}(t) \cos \left( 2 \pi f_n t + \phi_{P,n,m}(t) \right) \\
                        &= \Re \left\{ \sum_{n=1}^{N} x_{P,n,m}(t) e^{j2 \pi f_n t} \right\} \\
                        &= \Re \left\{ \sum_{n=1}^{N} w_{P,n,m} e^{j2 \pi f_n t} \right\}
                    \end{split}
                \end{equation}
                The corresponding power waveform vector is stacked across $M$ transmit antennas as
                \begin{equation} \label{eq:x_P(t)}
                    \boldsymbol{x}_P(t) = \Re \left\{ \sum_{n=1}^{N} \boldsymbol{w}_{P,n} e^{j2{\pi}{f_n}t} \right\}
                \end{equation}
                where $\boldsymbol{w}_{P,n}=[w_{P,n,1},\dots,w_{P,n,M}]^T$.
            \end{subsubsection}

            \begin{subsubsection} {Superposed Waveform}
                At time $t$, a superposition of the information and power waveform on antenna $m$ over subband $n$ writes as
                \begin{equation} \label{eq:x_{n,m}(t)}
                    \begin{split}
                        x_{n,m}(t)
                        &= x_{I,n,m}(t)+x_{P,n,m}(t) \\
                        &= w_{I,n,m} \tilde{x}_{I,n}(t)+w_{P,n,m}
                    \end{split}
                \end{equation}
                The transmitted signal on antenna $m$ at time $t$ is a summation over all subbands
                \begin{equation} \label{eq:x_m(t)}
                    \begin{split}
                        x_m(t)
                        &= x_{I,m}(t)+x_{P,m}(t) \\
                        &= \Re \left\{ \sum_{n=1}^{N} (w_{I,n,m} \tilde{x}_{I,n}(t)+w_{P,n,m}) e^{j2 \pi f_n t} \right\}
                    \end{split}
                \end{equation}
                Hence, the composite transmit signal vector is
                \begin{equation} \label{x(t)}
                    \begin{split}
                        \boldsymbol{x}(t)
                        &=\boldsymbol{x}_I(t)+\boldsymbol{x}_P(t) \\
                        &=\Re \left\{ \sum_{n=1}^{N} (\boldsymbol{w}_{I,n}\tilde{x}_n(t)+\boldsymbol{w}_{P,n}) e^{j2{\pi}{f_n}t} \right\}
                    \end{split}
                \end{equation}
            \end{subsubsection}

@@

        \begin{subsection} {Composite Channel Model}
            Consider a single-IRS scenario in a multipath environment. The frequency response of the AP-user (i.e. direct) channel between antenna $m$ and user $k$ at subband $n$ is $h_{D,n,m,k}=A_{D,n,m,k}e^{j\bar{\psi}_{D,n,m,k}}=\sum_{l_{D,k}=1}^{L_{D,k}} \alpha_{l_{D,k}} e^{j\left( -2 \pi f_n \tau_{l_{D,k}}+\varsigma_{l_{D,k},n,m,k} \right)}$, where $L_{D,k}$ is the number of paths in the direct link of user $k$, $\alpha_{l_{D,k}}$ and $\tau_{l_{D,k}}$ are the delay and amplitude gain of the $l_{D,k}$-th path, $\varsigma_{l_{D,k},n,m,k}$ is the phase shift of the $l_{D,k}$-path between transmit antenna $m$ and the receive antenna of user $k$ at subband $n$. Similarly, the AP-IRS (i.e. incident) channel between antenna $m$ and element $u$ at subband $n$ writes as $h_{I,n,m,u}=A_{I,n,m,u}e^{j\bar{\psi}_{I,n,m,u}}=\sum_{l_{I,u}=1}^{L_{I,u}} \alpha_{l_{I,u}} e^{j\left( -2 \pi f_n \tau_{l_{I,u}}+\varsigma_{l_{I,u},n,m,u} \right)}$, and the IRS-user (i.e. reflective) channel between element $u$ and user $k$ is $h_{R,n,u,k}=A_{R,n,u,k}e^{j\bar{\psi}_{R,n,u,k}}=\sum_{l_{R,k}=1}^{L_{R,k}} \alpha_{l_{R,k}} e^{j\left( -2 \pi f_n \tau_{l_{R,k}}+\varsigma_{l_{R,k},n,u,k} \right)}$. Assume that $\max_{l_{D,k} \neq l_{D,k}'} \lvert \tau_{l_{D,k}}-\tau_{l_{D,k}'} \rvert \ll 1/B_s$ and $\max_{l_{I,u},l_{R,k} \neq l_{I,u}',l_{R,k}'} \lvert \left( \tau_{l_{I,u}}+\tau_{l_{R,k}} \right)-\left( \tau_{l_{I,u}'}+\tau_{l_{R,k}'} \right) \rvert \ll 1/B_s$ such that $\tilde{x}_n(t)$ and $x_{n,m}(t)$ are narrowband signals, namely $\tilde{x}_n(t-\tau_{l_D}) = \tilde{x}_n(t-\tau_{l_{I}}-\tau_{l_R}) = \tilde{x}_n(t)$ and $x_{n,m}(t-\tau_{l_D}) = x_{n,m}(t-\tau_{l_{I}}-\tau_{l_R}) = x_{n,m}(t)$.

@@

        \begin{subsection} {Received Signal}
            In the signal received by user $k$, the component from transmit antenna $m$ captures the contribution of information and power waveforms through both direct and reflective links. It can be expressed as
            \begin{equation} \label{eq:y_{m,k}(t)}
                \begin{split}
                    y_{m,k}(t)
                    &= \Re \left\{ \sum_{n=1}^{N} \sum_{l_{D,k}=1}^{L_{D,k}} \alpha_{l_{D,k}} x_{n,m}(t-\tau_{l_{D,k}}) e^{j \left( -2 \pi f_n (t-\tau_{l_{D,k}})+\varsigma_{l_{D,k},n,m,k}\right) } \right\} \\
                    &\quad+ \Re \left\{ \sum_{n=1}^{N} \sum_{l_{R,k}=1}^{L_{R,k}} \sum_{u=1}^{U} \alpha_{l_{R,k}} r_u \alpha_{l_{I,u}} x_{n,m}(t-\tau_{l_{R,k}}-\tau_{l_{I,u}}) e^{j \left( -2 \pi f_n (t-\tau_{l_{R,k}}-\tau_{l_{I,u}})+\varsigma_{l_{R,k},n,u,k}+\varsigma_{l_{I,u},n,m,u}\right)} \right\} \\
                    &\approx \Re \left\{ \sum_{n=1}^{N} h_{D,n,m,k}(t) x_{n,m}(t) e^{j2 \pi f_n t} \right\} \\
                    &\quad+ \Re \left\{ \sum_{n=1}^{N} \sum_{u=1}^{U} h_{R,n,u,k}(t) r_u h_{I,n,m,u}(t) x_{n,m}(t) e^{j2 \pi f_n t} \right\} \\
                    &= \Re \left\{ \sum_{n=1}^{N} {s_{P,n,m}}{A_{D,n,m,k}} e^{j\left( 2{\pi}{f_n}{t}+\phi_{P,n,m}+\bar{\psi}_{D,n,m,k} \right)} \right\} \\
                    &\quad+ \Re \left\{ \sum_{n=1}^{N} \sum_{u=1}^{U} {s_{P,n,m}}{A_{R,n,u,k}}{\beta_u}{A_{I,n,m,u}} e^{j\left( 2{\pi}{f_n}{t}+\phi_{P,n,m}+\bar{\psi}_{R,n,u,k}+\theta_u+\bar{\psi}_{I,n,m,u} \right)} \right\} \\
                    &\quad+ \Re \left\{ \sum_{n=1}^{N} {\tilde{s}_{I,n,m}}{A_{D,n,m,k}} e^{j\left( 2{\pi}{f_n}{t}+\tilde{\phi}_{I,n,m}+\bar{\psi}_{D,n,m,k} \right)} \right\} \\
                    &\quad+ \Re \left\{ \sum_{n=1}^{N} \sum_{u=1}^{U} {\tilde{s}_{I,n,m}}{A_{R,n,u,k}}{\beta_u}{A_{I,n,m,u}} e^{j\left( 2{\pi}{f_n}{t}+\tilde{\phi}_{I,n,m}+\bar{\psi}_{R,n,u,k}+\theta_u+\bar{\psi}_{I,n,m,u} \right)} \right\}
                \end{split}
            \end{equation}
            Therefore, the RF signal input to the antenna at user $k$ is
            \begin{equation} \label{eq:y_{k}(t)}
                y_{k}(t) = \sum_{m=1}^{M} y_{m,k}(t)
            \end{equation}
        \end{subsection}
    \end{section}
